Multi-line Intensity Mapping

### 2019-07-15 paper/ms.tex
Small changes to abstract

\begin{abstract}
% Context
Intensity mapping of galactic emission lines stands to shed light on both
galactic astrophysics and cosmology in the coming years. Current efforts span
a wide range of redshifts, from $z\sim1$ to $z\sim10$, allowing pursuits of
key science goals out of reach of spectroscopic galaxy surveys and into the
uncertain astrophysics of the Epoch of Reionization.
% Aims
Cross-correlations of two different emission lines can confront many of the
observational challenges of line intensity mapping, most notably interloper
contamination. We aim to better our understanding when three or more lines are
combined through the cross-power spectrum.
% Methods
Using the Fisher matrix formalism, we develop a framework for understanding
the observational constraints possible with intensity mapping of an arbitrary
number of lines, considering both the cross-spectra alone and the auto- and
cross-spectra combined.
% Results
Results.
% Conclusions
We find that multi-line intensity mapping is a promising technique, and future
intensity mapping efforts should take care to maximize the shared area between
different surveys.
\end{abstract}

>>>>

\begin{abstract}
% Context
Intensity mapping of galactic emission lines stands to shed light on both
galactic astrophysics and cosmology from $z\sim1$ to $z\sim10$ in the coming
years. However, several observational challenges must first be met, including
the problems of interloper and foreground contamination.
% Aims
Cross-correlations of two different emission lines can confront these
challenges. By combining the cross-correlations between three or more lines,
one can measure the large-scale bias encoded in the auto-spectrum of each
line. We aim to understand the general case in more detail.
% Methods
Using the Fisher matrix formalism, we develop a framework for understanding
the observational constraints possible with intensity mapping of an arbitrary
number of lines and their associated cross-spectra.
% Results
Results.
% Conclusions
We find that multi-line intensity mapping is a promising technique, and future
intensity mapping efforts should take care to maximize the shared area between
different surveys.
\end{abstract}
